A new simplified manual tour, with examples in mathematica and R

### 2022-06-14 paper/paper.Rmd
make sure changes are committed

```{r manualsequence, outwidth="80%", width=12, height=5, fig.cap="Sequence of projections where contribution of one variable is controlled (black) is changed: (top) unconstrained orthonormalisation, (bottom) constrained as specified. The dot (orange) indicates the chosen values for the controlled variable. For the constrained orthonormalisation it can be seen to precisely match the axis, but not so for the unconstrained orthonormalisation."}
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

```{r }
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

    - `data`: A list of data matrices (they must all have the same dimensionality)
    - ``projmat`: A projection matrix which describes the projection plane. This is the 
initial projection and does not neet by orthonormal.
    - ``xRange`: A list which details the range of the horizontal axis.
    - ``yRange`: A list which details the range of the vertical axis.
    - ``colour`: A list of graphics directives to be applied to each data \
matrix.

@@

@@

Does this need to be a separate function from SlicePlot?

@@

I have found it useful to input different data sets rather than have this function sort them automatically using the last column.

@@

>>>>

```{r manualsequence, out.width="100%", width=12, height=4, fig.cap="Sequence of projections where contribution of one variable is controlled (black) is changed: (top) unconstrained orthonormalisation, (bottom) constrained as specified. The dot (orange) indicates the chosen values for the controlled variable. For the constrained orthonormalisation it can be seen to precisely match the axis, but not so for the unconstrained orthonormalisation."}
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

```{r othermethod, out.width="100%", width=12, height=4, fig.cap="Manual controls with algorithm 2. The precise location of the axis is maintained."}
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

    - `data`: A list of data matrices (they must all have the same dimensionality)
    - ``projmat`: A projection matrix which describes the projection plane. This is the 
initial projection and does not neet by orthonormal.
    - ``xRange`: A list which details the range of the horizontal axis.
    - ``yRange`: A list which details the range of the vertical axis.
    - ``colour`: A list of graphics directives to be applied to each data matrix.

@@

**It would be good if the initial projection matrix (and maybe the centre) had default values. Perhaps a random matrix with the correct dimensions read from the data?**

@@

**Does this need to be a separate function from SlicePlot?**

@@

**I have found it useful to input different data sets rather than have this function sort them automatically using the last column.**

@@

**We would need a screenshot (and video) for each of these.**

### 2022-06-14 paper/paper.tex
make sure changes are committed

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/manualsequence-1.pdf}
\caption{Sequence of projections where contribution of one variable is
controlled (black) is changed: (top) unconstrained orthonormalisation,
(bottom) constrained as specified. The dot (orange) indicates the chosen
values for the controlled variable. For the constrained
orthonormalisation it can be seen to precisely match the axis, but not
so for the unconstrained orthonormalisation.}
\end{figure}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}

@@

  \begin{itemize}
  \tightlist
  \item
    \texttt{data}: A list of data matrices (they must all have the same
    dimensionality)
  \item
    `\texttt{projmat}: A projection matrix which describes the
    projection plane. This is the initial projection and does not neet
    by orthonormal.
  \item
    `\texttt{xRange}: A list which details the range of the horizontal
    axis.
  \item
    `\texttt{yRange}: A list which details the range of the vertical
    axis.
  \item
    `\texttt{colour}: A list of graphics directives to be applied to
    each data\\
    matrix.
  \end{itemize}
\end{itemize}

@@

@@

@@

Does this need to be a separate function from SlicePlot?

I have found it useful to input different data sets rather than have
this function sort them automatically using the last column.

@@

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/manualsequence-1} \caption{Sequence of projections where contribution of one variable is controlled (black) is changed: (top) unconstrained orthonormalisation, (bottom) constrained as specified. The dot (orange) indicates the chosen values for the controlled variable. For the constrained orthonormalisation it can be seen to precisely match the axis, but not so for the unconstrained orthonormalisation.}\label{fig:manualsequence}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/othermethod-1} \caption{Manual controls with algorithm 2. The precise location of the axis is maintained.}\label{fig:othermethod}
\end{figure}

@@

  \begin{itemize}
  \tightlist
  \item
    \texttt{data}: A list of data matrices (they must all have the same
    dimensionality)
  \item
    `\texttt{projmat}: A projection matrix which describes the
    projection plane. This is the initial projection and does not neet
    by orthonormal.
  \item
    `\texttt{xRange}: A list which details the range of the horizontal
    axis.
  \item
    `\texttt{yRange}: A list which details the range of the vertical
    axis.
  \item
    `\texttt{colour}: A list of graphics directives to be applied to
    each data matrix.
  \end{itemize}
\end{itemize}

@@

\textbf{It would be good if the initial projection matrix (and maybe the
centre) had default values. Perhaps a random matrix with the correct
dimensions read from the data?}

@@

\textbf{It would be good if the initial projection matrix (and maybe the
centre) had default values. Perhaps a random matrix with the correct
dimensions read from the data?}

\textbf{Does this need to be a separate function from SlicePlot?}

@@

\textbf{I have found it useful to input different data sets rather than
have this function sort them automatically using the last column.}

@@

\textbf{We would need a screenshot (and video) for each of these.}
